Revisited hidden weight bit function

### 2024-10-29 RevisedHiddenWeight.tex

\subsection{Study of $\Dnka nka$ through generating functions}\label{sec:genfunc}
For $a\in\F_2^n$, we denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$. We then have $p+q+r=n/2$. 
We consider further the integer polynomial $P_a(z)$ given by the following expression:
\[
P_a(z)=(-z^2+2z+1)^{p}\cdot(-z^2-2z+1)^{q}\cdot(z^2+1)^{r}.
\]

@@

\begin{Prop}[Cauchy's estimate \eg~\cite{rudin1987}, Theorem 10.26]\label{property:cauchy_estimate}
    Let $w$ be a complex number, and let $R>0$ be some radius. If $f$ is a holomorphic function defined on an open set containing every complex number $z$ satisfying $|z-w|<R$, then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, as follows:
    \[
        \left|\frac{\dd^k}{\dd^k z}f(w)\right|\leq\frac{k!\cdot M_R}{R^k},
    \]
    where $M_R$ is the maximum of $|f(z)|$ on the circle $|z-w|=R$.
\end{Prop}

@@

>>>>

\subsection{Study of $\Dnka nka$ through Generating Functions}\label{sec:genfunc}

\begin{definition}\label{defi:P_a}
    For $a\in\F_2^n$, denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$. We then have $p+q+r=n/2$. Consider further the integer polynomial $P_a(z)$ given by the following expression:
    \[
    P_a(z)=(-z^2+2z+1)^{p}\cdot(-z^2-2z+1)^{q}\cdot(z^2+1)^{r}.
    \]
\end{definition}

@@

\begin{Prop}[Cauchy's estimate \eg~\cite{rudin1987}, Theorem 10.26]\label{property:cauchy_estimate}
    Let $w$ be a complex number, and let $R>0$ be some radius. If $f$ is a holomorphic function defined on an open set containing every complex number $z$ satisfying $|z-w|<R$, then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, as follows:
    \[
        \left|\frac{\dd^k}{\dd^k z}f(z)\vert_{z=w}\right|\leq\frac{k!\cdot M_R}{R^k},
    \]
    where $M_R$ is the maximum of $|f(z)|$ on the circle $|z-w|=R$.
\end{Prop}

@@

When one is given an explicit value for $t$ in terms of $n$, one can be more careful when employing the proof strategy of Theorem~\ref{theorem:bound_D_nka_generalized}. Let us for instance consider the case $t=n/3$:

\begin{proposition}\label{proposition:walsh_t_over_3}
    Let $n\in\N$ be divisible by $6$. Then for every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
    \[
        |\wtk{d_{n/3,n}}{k}(a)|\leq2^{3n/4},\quad|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}.
    \]
\end{proposition}

\begin{proof}
    As before, we want to bound the maximum of $|P_{a,t}(z)|$ on $|z|=1$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[0,n]$. Write $a=(b,c)$ with $b\in\F_2^{2t}$ and let $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}. Since we want to find a bound of $|P_{a,t}(z)|$ on $|z|=1$ which works for all $a\in\F_2^n$, it makes sense to only consider those $a$ which are actually candidates for maximizing $|P_{a,t}(z)|$, namely those for which only one among $(p,q,r)$ is non-zero, and for which only one among $(u,v)$ is non-zero. This leaves us with the following cases to consider for $(p,q,r;u,v)$:
    \begin{gather*}
        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0),\\
         (t,0,0;0,n-2t),\quad(0,t,0;0,n-2t),\quad(0,0,t;0,n-2t).
    \end{gather*}
    Since swapping both $(p,q)$ and $(u,v)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $|z|=1$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
    \[
        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0).
    \]
    Let us for instance find an upper bound of $|P_{a,t}(z)|$ in case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $n-2t=t$ by assumption, we get:
    \[
        P_{a,t}(z)=[(-z^2+2z+1)(1+z)]^t.
    \]
    Writing $z=\cos\alpha+\mathrm i\sin\alpha$, we obtain:
    \[
        |P_{a,t}(z)|^2=[(6-2\cos2\alpha)(2+2\cos\alpha)]^t.
    \]
    Through calculus, one finds that $|(6-2\cos2\alpha)(2+2\cos\alpha)|<2^{9/2}$, and hence that $|P_{a,t}(z)|<2^{9t/4}=2^{3n/4}$. The same upper bound works for the remaining two candidates for $(p,q,r;u,v)$, and we can therefore conclude that $|\wtk{d_{n/3,n}}{k}(a)|\leq 2^{3n/4}$ and that $|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}$.
\end{proof}

\begin{remark}
    The proof of Proposition~\ref{proposition:walsh_t_over_3} can be redone for other values of $t$. In Figure~\ref{fig:walsh_bounds_generalization}, we provide bounds of the form $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$, where $\alpha\in[0,20]$ is represented on the $x$-axis and $\beta$ is represented on the $y$-axis. 
\end{remark}

\begin{figure}
	\centering
	\includegraphics[width=9cm]{walsh_bounds_generalization.pdf}
	\caption{For each point $(\alpha,\beta)$, we have $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$.}
    \label{fig:walsh_bounds_generalization}
\end{figure}
